---
title: "vis_i"
subtitle: "Part I"
output: github_document
---

```{r setup}
library(tidyverse)
library(ggridges)
```

## Load the weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
weather_df
```

## Scatter Plot

Create my first scatterplot ever.

```{r}
ggplot(weather_df,aes(x = tmin, y = tmax)) +
  geom_point()
```

New Approach, same plot

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```

Save and edit a plot object

```{r}
weather_plot = 
  weather_df %>%
  ggplot(aes(x = tmin, y = tmax))

weather_plot + geom_point()
```

## Advanced scatterplot

Start with the same one and make it fancy

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color  = name)) +
  geom_point() + 
  geom_smooth(se = FALSE) #add smooth trajectory
```

What about the 'aes' placement?

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +  
  geom_point(aes(color = name)) +
  geom_smooth()
#color only applied to scatter plot
```

Let's facet some things

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color  = name)) +
  geom_point(alpha = .2) +  #alpha: add transparency; could be sent to some variable
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
# . means don't create rows, but create columns
```

Let's combine some elements and try a new plot.

```{r}
weather_df %>%
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp),alpha = .5) + # prcp = precipitation
  geom_smooth(se = FALSE)+
  facet_grid(. ~ name)

```

## some small notes

How many geoms have to exist?

You can have whatever geoms you want.

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_smooth(se = FALSE)
```

You can use a neat geom!

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax))+
  #geom_hex()
  geom_density2d()+
  geom_point(alpha = .3)
```

## Univariate plots

Histogram are really great.

```{r}
weather_df %>%
  ggplot(aes(x = tmin)) +
  geom_histogram()
```

Can we add color?

```{r}
weather_df %>%
  ggplot(aes(x = tmin, fill = name)) +
  #geom_histogram(position = "dodge")
  geom_histogram() +
  facet_grid(. ~ name)
```

Let's try a new geometry

```{r}
weather_df %>%
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = .3)
```

What about box plots?

```{r}
weather_df %>%
  ggplot(aes(x = name, y = tmin)) + #give a categorical variable on the x axis
  geom_boxplot()
```

Trendy plots

```{r}
weather_df %>%
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_violin(alpha = .5) + 
  stat_summary()
  #by default give the mean and standard error in both directions
  #stat_summary(fun = "median")
```

Ridge plots -- the most popular plot of 2017

useful for specific circumstances

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = name)) +
  geom_density_ridges()
```

## save and embed

let's save a scatter plot

```{r}
weather_plot = 
  weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5)

ggsave("./results/weather_plot.pdf", weather_plot, width = 8, height = 5)
```

What about embedding?

```{r, fig.width = 6, fig.height = 3}
weather_plot
```

Embed at different size.
```{r,fig.width = 12, fig.height = 6}
weather_plot
```